The \dealii Library, Version 9.2

### 2020-05-25 9.2/paper.tex
Update one bib entry.
add to author list

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

% \author[3]{Thomas~C.~Clevenger}
% \affil[3]{School of Mathematical and Statistical Sciences,
%   Clemson University,
%   Clemson, SC, 29634, USA
%   {\texttt{\{tcleven, heister\}@clemson.edu}}}
%
% \author[4]{Denis~Davydov}
% \affil[4]{Chair of Applied Mechanics,
%   Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen, Germany.
%   {\texttt{\{denis.davydov,jean-paul.pelteret\}@fau.de}}}
%
\author[5]{Marc~Fehling}
\affil[5]{Institute for Advanced Simulation,
  Forschungszentrum J\"{u}lich GmbH,
  52425 J\"{u}lich, Germany.
  {\texttt{m.fehling@fz-juelich.de}}}
%
% \author[6]{Daniel Garcia-Sanchez}
% \affil[6]{Sorbonne Universit\'es, UPMC Univ.\ Paris 06, CNRS-UMR 7588,
%   Institut des NanoSciences de Paris, F-75005, Paris, France
%   {\texttt{daniel.garcia-sanchez@insp.upmc.fr}}}
%
% \author[2]{Graham Harper}
%
\author[3]{Timo~Heister}
 \affil[3]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister@clemson.edu}}}

@@

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For curved geometry representations and manifolds:
   \cite{HeltaiBangerthKronbichlerMola2019};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For Boundary Elements Computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
   \item For uses of the \texttt{ParameterAcceptor} concept, the
     \texttt{MeshWorker::ScratchData} base class, and the
     \texttt{ParsedConvergenceTable} class: \cite{SartoriGiulianiBardelloni-2018-a}.
\end{itemize}

\todo[inline]{Need to add the particles paper by Gassmoeller et al.}

>>>>

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

 \author[3]{Thomas~C.~Clevenger}
 \affil[3]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{tcleven/heister@clemson.edu}}}
%
% \author[4]{Denis~Davydov}
% \affil[4]{Chair of Applied Mechanics,
%   Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen, Germany.
%   {\texttt{\{denis.davydov,jean-paul.pelteret\}@fau.de}}}
%
\author[5]{Marc~Fehling}
\affil[5]{Institute for Advanced Simulation,
  Forschungszentrum J\"{u}lich GmbH,
  52425 J\"{u}lich, Germany.
  {\texttt{m.fehling@fz-juelich.de}}}
%
% \author[6]{Daniel Garcia-Sanchez}
% \affil[6]{Sorbonne Universit\'es, UPMC Univ.\ Paris 06, CNRS-UMR 7588,
%   Institut des NanoSciences de Paris, F-75005, Paris, France
%   {\texttt{daniel.garcia-sanchez@insp.upmc.fr}}}
%
% \author[2]{Graham Harper}
%
\author[3]{Timo~Heister}

@@

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For curved geometry representations and manifolds:
   \cite{HeltaiBangerthKronbichlerMola2019};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For boundary element computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
   \item For uses of the \texttt{ParameterAcceptor} concept, the
     \texttt{MeshWorker::ScratchData} base class, and the
     \texttt{ParsedConvergenceTable} class:
     \cite{SartoriGiulianiBardelloni-2018-a};
   \item For uses of the particle functionality in \dealii{}: \cite{GLHPB18}.
\end{itemize}
